The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Changes the the nu section of the paper

We now consider the {\tt nu} function, which plays a fundamental role in this package.  In addition to describing its basic functionality, we also discuss its theoretical foundations, including its relationship the {\tt fpt} function consider in Section \ref{sec.FPT}.

Here, we work in a polynomial ring over a finite field of characteristic $p>0$.  All ideals and polynomials under consideration are regarded in this ambient ring.

If $f$ is a polynomial contained in the radical of an ideal $J$, and $e$ is a natural number, then the command {\tt nu(e,f,J)} outputs the maximal integer exponent $n$ such that $f^{ n}$ is not contained in $J^{[p^e]}$.  Here, $J^{[p^e]}$ denotes the $p^e$-th Frobenius power of $J$, that is, the ideal generated by the $p^e$-th powers of the elements of $J$.

More generally, if $I$ is an ideal contained in the radical of $J$, then {\tt nu(e,I,J)} outputs the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.

The outputs of {\tt nu(e,f,J)} and {\tt nu(e,I,J)} are denoted $\nu_f^J(p^e)$ and $\nu_I^J(p^e)$, respectively, in the literature, and were originally defined in the paper \cite{MustataTakagiWatanabeFThresholdsAndBernsteinSato}.

@@

We highlight some degenerate cases:  Suppose that $e$ is a natural number.  If $f$ is zero, then the output of {\tt nu(e,f,J)} is {\tt 0}, and if $f$ is not contained in the radical of $J$, then the output is instead {\tt infinity}.  These degenerate cases extend analogously to the outputs of {\tt nu(e,I,J)} when $I$ is an ideal.

>>>>

We now consider the {\tt nu} function, which is fundamental.   As in the introduction, we work in a polynomial ring over a finite field of characteristic $p>0$.

Fix a natural number $e$.  If $f$ is polynomial contained in the radical of an ideal $J$, then the command {\tt nu(e,f,J)} outputs $\nu_f^J(p^e)$, the maximal integer exponent such that $f^n$ is not contained in $J^{[p^e]}$.  More generally, if $I$ is an ideal contained in the radical of $J$, then {\tt nu(e,I,J)} outputs $\nu_I^J(p^e)$, the maximal integer exponent $n$ such that $I^n$ is not contained in $J^{[p^e]}$.

@@

We highlight some degenerate cases:  If $f$ is zero, then the output of {\tt nu(e,f,J)} is {\tt 0}, and if $f$ is not contained in the radical of $J$, then the output is instead {\tt infinity}.  These degenerate cases extend analogously to {\tt nu(e,I,J)} when $I$ is an ideal.
